\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Working groups are by definition on-chain, so some of that is definitely not off-chain.
Fix typo

There are a number of key infrastructure dynamics, such as entry and exit of actors into the roles as distributors or storage providers, and also updating what are assigned to what data. These are all initiated and coordinated through off-chain messaging protocols, and honest conduct is expected purely on governance sanctions. This will be described in further detail in the future.

@@

Many protocols suffer from the lack of an endogenous financing mechanism, and stateless protocols cannot have them by definition. Even in many statefull protocols, key contributors end up either severly underfunded, which is detrimental to quality and development progress, or they rely on third part revenue sources which do not have incentives that are guided by the interests of all protocol stakeholders.

>>>>

There are a number of key infrastructure dynamics, such as entry and exit of actors into the roles as distributors or storage providers, and also updating what are assigned to what data. These may be initiated and coordinated through off-chain messaging protocols, and honest conduct is expected purely on governance sanctions. This will be described in further detail in the future.

@@

Many protocols suffer from the lack of an endogenous financing mechanism, and stateless protocols cannot have them by definition. Even in many stateful protocols, key contributors end up either severly underfunded, which is detrimental to quality and development progress, or they rely on third part revenue sources which do not have incentives that are guided by the interests of all protocol stakeholders.
